---
title: "Proposal"
author: "Joanna Fang, Wenjin Jiang, Eri Jibiki, Roy Song, Michael Wang, Kate Zhang"
date: '2024-02-29'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, include = TRUE, message = FALSE, warning = FALSE)
```

```{r}
# load packages
library(tidyverse)
library(dplyr)
library(knitr)
library(broom)
library(ggplot2)
```


# Data Sets

• Describe the list of data sets you are thinking for the final project.

## Starbucks Customer Satisfactory Survey

### Introduction 

This dataset, titled 'Starbucks Customer Survey,' is originally from Kaggle (https://www.kaggle.com/datasets/mahirahmzh/starbucks-customer-retention-malaysia-survey/data). It consists of survey responses from over 100 participants regarding their purchasing behavior at Starbucks in Malaysia. Incomes are shown in Malaysian Ringgit (RM). The dataset includes 33 variables, covering demographic information about the customers—such as gender, age range, employment status, and income range—as well as their current behavior in purchasing from Starbucks, including the products purchased and the amount of money spent.


```{r cars}
# import data
starbucks_data <- read.csv("Starbucks satisfactory survey encode cleaned.csv")
```

### Variables Description

[to be added]

### Questions to Explore

- What are the factors influencing Loyalty Program Enrollment and how can we further increase the enrollment rate in the future?
- How can we increase customer's time spent in the store and money spent in Starbuck's products?
- What are some future in-store campaigns to increase customer loyalty and money spending?

### Data Exploration

Since the dataset is relatively small. We will run a preliminary regression to see if there are enough significant coefficients.


```{r}
logit <- glm(membershipCard ~ ., family=binomial,data=starbucks_data)
tidy(logit) %>% kable(digits = 2)
```


```{r echo=FALSE}
backward_select <- step(logit, scope = formula(logit),
                        direction = "backward")
```

```{r}
logit2 <- glm(membershipCard ~ income + location + productRate + priceRate + 
    serviceRate + promoMethodOthers + loyal, family=binomial,data=starbucks_data)
tidy(logit2) %>% kable(digits = 2)
```





